---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jirarest

<!-- badges: start -->
<!-- badges: end -->

The goal of jirarest is to provide a REST API in R for accessing the BCGSC Jira ticketing system.

## Installation

You can install the development version of jirarest from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("TalhoukLab/jirarest")
```

## Examples

Here are examples of the currently implemented resources.

### Create Issue

An issue can be created within a Jira project.

```{r create-issue, eval=FALSE}
library(jirarest)
create_issue(project = "BC",
             summary = "new analysis",
             description = "analysis for someone")
```

### Add Comment

We can add comments to existing issues. Assumes that the current working directory is the name of issue.

```{r add-comment, eval=FALSE}
add_comment("report completed")
```

### Attach File

Files such as PDF reports and data can be attached to issues.

```{r attach-file, eval=FALSE}
attach_file("/path/to/file")
```
